---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# fitzRoy

The goal of fitzRoy is to provide a set of functions that allows for users to easily get access to AFL data from sources such as afltables.com and footywire.com. There are also tools for processing and cleaning that data. Future versions will include basic ELO processing functions. 

## Installation

You can install fitzRoy from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jimmyday12/fitzRoy")
library(fitzRoy)
```

## Usage

The `fitzRoy` package can be used to simply get data from various sources. Some minimal working examples are below.

### Getting Data

Primarily, the tool can be used to access data from various sources. Data is included in the package and can be access directly however this will not be up to date. Each source of data has functions for updating data during the season. 


### Footywire
Footywire data is available in the form of advanced player match statistics from 2010 games onwards. This is when advanced statistics became available.

Footywire data from 2010-2017 is included in the package. This will be updated periodically but you will need to update your R package to get access to the latest data.

```{r footywire}
## Show the top of player_stats
# head(player_stats)
```

We can also use the `update_footywire_stats` function to get the most up to date data. This will merge data from 2010-2017 with any new data points. 

```{r update_footywire}
## Update footywire data
# dat <- update_footywire_stats()

# tail(dat)
```




---
Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
