---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# fitzRoy

The goal of fitzRoy is to provide a set of functions that allows for users to easily get access to AFL data from sources such as afltables.com and footywire.com. There are also tools for processing and cleaning that data. Future versions will include basic ELO processing functions. 

## Installation

You can install fitzRoy from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jimmyday12/fitzRoy")
library(fitzRoy)
```

## Usage

The `fitzRoy` package can be used to simply get data from various sources. Some minimal working examples are below.

### Getting Data

Primarily, the tool can be used to access data from various sources. Data is included in the package and can be access directly however this will not be up to date. Each source of data has functions for updating data during the season. 

### AFL Tables match results
You can access the basic afl tables match results data. This includes all matches from 1897-current. It is generally updated on the day after a round finishes. 

You can access the data directly from the package using `match_results`. This will be updated periodically but you will need to update your R package to get access to the latest data. It is better to use `get_match_results` directly, as this will give you up to date results.

```{r results}
library(fitzRoy)
results <- get_match_results()

tail(results)

```

You can also convert this format into a more analysis friendly "long" format using the helper function `convert_results`. 

```{r convert}
results_long <- convert_results(results)

head(results_long)
```

### Fixture
You can access the fixture using `get_fixture` function. This will download the fixture for the current calendar year by default. 

```{r fixture}
fixture <- get_fixture()

head(fixture)
```
### Footywire Advanced Player Stats
Footywire data is available in the form of advanced player match statistics from 2010 games onwards. This is when advanced statistics became available.

Footywire data from 2010-2017 is included in the package. This will be updated periodically but you will need to update your R package to get access to the latest data.

```{r footywire}
## Show the top of player_stats
head(fitzRoy::player_stats)
```

We can also use the `update_footywire_stats` function to get the most up to date data. This will merge data from 2010-current with any new data points. 

```{r update_footywire}
## Update footywire data
dat <- update_footywire_stats()

tail(dat)
```


### Weather
We have also included weather data for the 2017 season. This is a work in progress but includes rainfall data from the nearest observation station to each ground. This data is included in the package as `results_weather`.

```{r weather, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

# Get 2017 weather data
weather <- fitzRoy::results_weather %>%
  filter(Season == 2017)

# Plot total rainfal for each home team
ggplot(dat = weather, aes(x = Home.Team, y = Rainfall)) +
  geom_col() + 
  coord_flip()

```
### Squiggle Data
You can access data from the [Squiggle API](api.squiggle.com.au) where the tips of well known AFL tipping models are collected. See full instructions on the above link. 

```{r squiggle1, message=FALSE, warning=FALSE}
# You can get the sources
sources <- get_squiggle_data("sources")
head(sources)
```

```{r squiggle2, message=FALSE, warning=FALSE}
# Get all tips
tips <- get_squiggle_data("tips")
head(tips)  
```

```{r squiggle3, message=FALSE, warning=FALSE}
# Get` just tips from round 1, 2018
tips <- get_squiggle_data("tips", round = 1, year = 2018)
head(tips)
```
---
Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
