---
title: "Docker Support"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Docker Support}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fitzRoy)
```

## Docker Support

fitzRoy now provides [Docker](https://www.docker.com/get-started) support in the form of an image hosted on [DockerHub](https://hub.docker.com/r/jimmyday12/fitzroy/).

### Usage
 
Once you have the images, (e.g. `docker pull jimmyday12/fitzroy:latest`) run one of the following commands.

* To start [RStudio](https://rstudio.com/) with Fitzroy ready to use:
  * `docker run -d -p 8787:8787 --name fitzroy jimmyday12/fitzroy:latest` and open `http://localhost:8787`.  *(Username: `rstudio`, Password: `rstudio`)
* To start an R terminal prompt with fitzRoy ready to use:
  * `docker run -it jimmyday12/fitzroy:latest R` to start with an R terminal prompt.
  * Run `quit()` to exit the container

### Building the image locally

To build the Docker image run the following from the root of the repository.

* `docker build -t jimmyday12/fitzroy:latest -f docker/rstudio/Dockerfile .`

