---
title: "Introduction to fitRoy"
description: >
  Learn how to get started with the basics of fitzRoy
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fitRoy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo=FALSE}
not_cran = identical(Sys.getenv("NOT_CRAN"), "true")
online <- !is.null(curl::nslookup("r-project.org", error = FALSE))
eval_param <- not_cran & online


knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
```

The goal of fitzRoy is to make it easy to access data from the AFLM and AFLW competitions. It provides a simple and consistent API to access data such as match results, fixtures and player statistics from multiple data sources. 

```{r}
library(dplyr)
library(fitzRoy)
```
## Fetching Data
Primarily, `fitzRoy` can be used to access data from various sources using the `fetch_` functions. For a detailed view on how the API works - view the [Main Fetch Functions]() vignette. 

## Good practices
In most cases, trying to use the same source for all of your analysis will be most beneficial. This is not always possible as some sources only go back so far (the AFL website only has data back to 2011), while some data is not available (AFL Tables doesn't have decent fixture data). If you are mixing sources, be careful to understand differences in naming structures, team names and player names. 

It is also a good idea to avoid regularly calling whole datasets. Where possible, try to keep an off-line version of your data and only request the smallest amount possible to get the new data you require. This is both faster (less data transferred over your Internet connection and less data living in your memory) but also helps to reduce traffic on the data providers servers. 

## Examples
### Fixture
Fixture data is available from multiple places. The most reliable and complete data usually comes from the AFL website. From that website you can specify either the Mens or Womens competitions using the `comp` argument. 

```{r fixture, include=TRUE, eval=FALSE}
fixture <- fetch_fixture(2021, comp = "AFLW")
fixture %>%
  select(utcStartTime, round.name, 
         home.team.name, away.team.name, venue.name)
```
```{r fixture_included, echo=FALSE, eval=eval_param}
fixture <- fitzRoy:::fixture_afl_aflw_2021 
fixture %>%
  select(utcStartTime, round.name, 
         home.team.name, away.team.name, venue.name)
```

If wanted, you could return just a single round.
```{r fixture2, include=TRUE, eval=FALSE}
fetch_fixture(2021, round_number = 5, comp = "AFLM") %>%
  select(utcStartTime, round.name, 
         home.team.name, away.team.name, venue.name)

```
```{r fixture2_included, echo=FALSE, eval=eval_param}
fitzRoy:::fixture_afl_aflm_2021 %>%
  filter(round.roundNumber == 5) %>%
    select(utcStartTime, round.name, 
         home.team.name, away.team.name, venue.name)

```


You can get results data from other sources including `Squiggle` and `Footywire`. The default source for `fetch_results()` is the AFL.com.au website. 

```{r fixture_all, eval=FALSE}
fixture_afl <- fetch_fixture(2020)
fixture_aflw <- fetch_fixture(2020, round_number = 1, comp = "AFLW")
fixture_squiggle <- fetch_fixture_squiggle(2020, round_number = 10)
fixture_footywire <- fetch_fixture_squiggle(2018)
```

### Lineup
You can get the lineup for a particular round. This is usually useful when running after the teams have been announced but before the match has been played. 

The only data source with lineup data is the AFL.com.au website. 

```{r lineup, include=TRUE, eval=FALSE}
fetch_lineup(2021, round_number = 1, comp = "AFLW") %>%
  select(round.name, status, teamName, 
         player.playerName.givenName,
         player.playerName.surname, teamStatus)
```

```{r lineup_included, echo=FALSE, eval=eval_param}
fitzRoy:::lineup_aflw_2021_1 %>%
  select(round.name, status, teamName, 
         player.playerName.givenName,
         player.playerName.surname, teamStatus)
```

### Results
You can access AFL match results data from various sources. The most complete is the [AFL Tables](http://www.afltables.com) data, which includes all matches from 1897-current. 

```{r results, include=TRUE, eval=FALSE}
results <- fetch_match_results_afltables(1897:2019)
results
```
```{r results_included, echo=FALSE, eval=eval_param}
results <- fitzRoy:::results_afltables_all %>%
  filter(Date < "2020-01-01")

results
```

While it is possible to return all historical data, it is usually good practice to only return a small amount of data - such as a single season or round - and keep your own offline database of historical data. 

```{r results2, include=TRUE, eval=FALSE}
results_new <- fetch_results_afltables(2021)
bind_rows(results, results_new)
```
```{r results2_included, echo=FALSE, eval=eval_param}
results_new <- fitzRoy:::results_afltables_all %>%
  filter(Date >= "2020-01-01")

bind_rows(results, results_new)
```


You can get results data from other sources including `AFL`, `Squiggle` and `Footywire`. The default source for `fetch_results()` is the AFL.com.au website. 

```{r results-all, eval=FALSE}
results_afl <- fetch_results(2020, round_number = 11)
results_aflw <- fetch_results(2020, comp = "AFLW")
results_squiggle <- fetch_results_squiggle(2019, round_number = 1)
results_footywire <- fetch_results_footywire(1990)
```

You can get AFLW results by using the `comp` argument.

```{r results_aflw, include=TRUE, eval=FALSE}
fetch_results(2020, comp = "AFLW") %>%
  select(match.name, venue.name, round.name,
         homeTeamScore.matchScore.totalScore,
         awayTeamScore.matchScore.totalScore)
```
```{r results__afl2_included, echo=FALSE, eval=eval_param}
fitzRoy:::results_afl_aflw_2020 %>%
  select(match.name, venue.name, round.name,
         homeTeamScore.matchScore.totalScore,
         awayTeamScore.matchScore.totalScore)
```

### Ladder

The ladder for a particular round can be returned using `fetch_ladder`. Usually this only makes sense to return for one round at a time, although it is possible to return multiple rounds. 

```{r ladder, include=TRUE, eval=FALSE}
ladder <- fetch_ladder(2020, round_number = 7, comp = "AFLW") %>%
  select(season, round_name, position, 
         team.name, pointsFor, pointsAgainst, form)
ladder
```
```{r ladder_included, echo=FALSE, eval=eval_param}
ladder <- fitzRoy:::ladder_afl_aflw_2020 %>%
  select(season, round_name, position, 
         team.name, pointsFor, pointsAgainst, form)
ladder
```
There are many variables included in the AFL.com.au ladder. 


```{r ladder2, include=TRUE, eval=FALSE}
ladder <- fetch_ladder(2020, round_number = 7, comp = "AFLW")
ncol(ladder)
```
```{r ladder2_included, echo=FALSE, eval=eval_param}
ncol(fitzRoy:::ladder_afl_aflw_2020)

```

You can get ladder data from other sources including `Squiggle` and `Afltables`. The default source for `fetch_ladder()` is the AFL.com.au website. 

```{r ladder-all, eval=FALSE}
ladder_afl <- fetch_ladder(2020, round_number = 11)
ladder_aflw <- fetch_ladder(2020, comp = "AFLW")
ladder_squiggle <- fetch_ladder_squiggle(2019, round_number = 1)
ladder_afltables <- fetch_ladder_afltables(1990)
```

### Stats

We can return player statistics for a set of matches. The exact stats that are included varies quite a bit between data sources. 

The default is again the AFL.com.au which is fairly comprehensive. 

```{r stats, include=TRUE, eval=FALSE}
fetch_player_stats(2020, comp = "AFLW")
```
```{r stats_included, echo=FALSE, eval=eval_param}
fitzRoy:::stats_afl_aflw_2020
```

We also have detailed player stats courtesty of Fryzigg.

```{r stats2, include=TRUE, eval=FALSE}
fetch_player_stats(2019, source = "fryzigg")
```
```{r stats2_included, echo=FALSE, eval=eval_param}
fitzRoy:::stats_fryzigg_2019
```

Other providers include Afltables and Footywire. 

```{r stats-all, eval=FALSE}
stats_afl <- fetch_player_stats(2020, round_number = 11)
stats_aflw <- fetch_player_stats(2020, source = "AFL", comp = "AFLW")
stats_footywire <- fetch_player_stats(2019, round_number = 1, source = "footywire")
stats_afltables <- fetch_player_stats_afltables(1990)
```

### API's


