---
title: "Womens' AFL Stats"
author: "Oscar Lane"
date: "`r Sys.Date()`"
output: github_document
vignette: >
  %\VignetteIndexEntry{Womens' AFL Stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r gh-installation, eval = FALSE, echo = TRUE}
# install.packages("devtools")
devtools::install_github("jimmyday12/fitzRoy")
```

### Match data

```{r libraries, message=FALSE, warning=FALSE}
library(fitzRoy)
library(dplyr)
library(magrittr)
```

We can use the `get_aflw_match_data()` function to retrieve match data for all
matches.

```{r fetch_match_stats, message=FALSE, warning=TRUE}
match_data <- get_aflw_match_data()
```

Note that we are getting a few warnings: this is to tell us that the fixture has 
been downloaded for 2019, but no match data is available yet. Note that you will 
not be able to retrieve detailed stats for these games, so make sure you don't 
try to request detailed stats for these match IDs.

```{r show_match_stats, message=FALSE, warning=FALSE}
glimpse(match_data)
```

### Detailed stats

The `get_aflw_detailed_data()` can be used to return more detailed data than the
match data shown above. It takes a vector of match IDs as an argument. For
example, let's say we want detailed stats for the first 10 games in `match_data`
above. Then we would do:

```{r first_10, message=FALSE, warning=FALSE}
first10 <- head(match_data, 10) %>% 
  pull(Match.Id)
first10
```


```{r detailed_data, message=FALSE, warning=FALSE}
detailed_data <- get_aflw_detailed_data(matchids = first10)
detailed_data %>% glimpse
```



