---
title: "Womens' AFL Stats"
author: "Oscar Lane <lane.oscar@gmail.com>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Womens' AFL Stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Authentication

The AFL Stats website requires a cookie to retrieve data through GET requests.
The `get_womens_cookie()` function retrieves this cookie as a string. It
requires no arguments.

```{r, message=FALSE}
library(fitzRoy)
library(dplyr)
library(magrittr)
cookie <- get_aflw_cookie()
cookie
```

### Round list

The `get_rounds` function looks for available data. There is currently only 
2017 and 2018 data present, but the function will look for all years up to 2100.
(This is built as a while loop so it will cut off if it finds that it is
getting null responses, as it does for 2019 onwards at the moment, but it should
be relatively future-proof, given the site API doesn't change.)

```{r}
rounds <- get_aflw_rounds(cookie)
glimpse(rounds)
```

There are 16 observations, as there have been two seasons with 8 rounds each.

### Match data

We can use the `get_aflw_match_data()` function to retrieve match data for all
matches. Under the hood, this works by taking the `roundId` in the round list 
above, and using the internal `get_match_data()` function.

This could be extended to take a year argument, so that only games in
specified years are downloaded. There are only two seasons so far in the womens'
league, however, so we probably do want all the data!

```{r}
match_data <- get_aflw_match_data()
glimpse(match_data)
```

### Detailed stats

The `get_aflw_detailed_data()` can be used to return more detailed data than the
match data shown above. It takes a vector of match IDs as an argument. For
example, let's say we want detailed stats for the last 10 games in `match_data`
above. Then we would do:

```{r}
last10 <- tail(match_data, 10) %>% 
  pull(Match.Id)
last10
```


```{r}
detailed_data <- get_aflw_detailed_data(matchids = last10, cookie)
detailed_data %>% glimpse
```



