---
title: "Womens' AFL Stats"
author: "Oscar Lane"
date: "`r Sys.Date()`"
output: github_document
vignette: >
  %\VignetteIndexEntry{Womens' AFL Stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r gh-installation, eval = FALSE, echo = TRUE}
# install.packages("devtools")
# devtools::install_github("jimmyday12/fitzRoy")
```

### Match data

```{r libraries, message=FALSE, warning=FALSE}
library(fitzRoy)
library(dplyr)
```

We can use the `get_aflw_match_data()` function to retrieve match data for all
matches.

```{r fetch_match_stats, message=FALSE, warning=TRUE,}
match_data <- get_aflw_match_data()
```

Note that there will be warnings if a fixture is available but no match data has
been added yet. If this is the case, make sure you don't try to request detailed
match stats for these match IDs. 

```{r show_match_stats, message=FALSE, warning=FALSE}
glimpse(match_data)
```

### Detailed stats

The `get_aflw_detailed_data()` can be used to return more detailed data than the
match data shown above. It takes a vector of match IDs as an argument. For
example, let's say we want detailed stats for the first 10 games in `match_data`
above. Then we would do:

```{r first_10, message=FALSE, warning=FALSE}
first10 <- head(match_data, 10)
first10_ids <- first10$Match.Id
first10_ids
```

```{r}
detailed <- get_aflw_detailed_data(first10_ids)
glimpse(detailed)
```

